Considering scale in multilayer animal social networks

### 2020-06-15 paper/manuscript.Rmd
combine more mov
tidy

Another extension of multilayer networks using GPS location data is integrating
movement. Given the existing framework for constructing multilayer networks from
behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
quantify movement parameters could be integrated. For example, edges could
represent measures of dyadic or collective movement based on dynamic interaction
metrics [@Long_2014]. Integrating movement layers with habitat-specific social
association layers could further illuminate the role of movement as a driver
of the social and spatial environments an individual experiences [@Webber_2018].
We generated multilayer networks based on habitat-specific layers of 
social association. Coordinated movement of dyads, or groups, could vary based on
habitat, and the approach we outline could be used to explore mechanisms linking
the social and spatial environments. For example, social processes may be an
emergent property of the landscape because animals aggregate at resources, such
as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
patches or territories can also contribute to the formation of the social
environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
males interacted primarily at home range edges, presumably driving territorial
behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
network framework is a logical next step for a burgeoning field. In particular,
when association networks are habitat-specific, we suggest the integration of
movement and space use in multilayer networks provides novel insights into the
effects of habitat configuration on the formation of the social environment
[@He_2019; @Webber_2018].

@@

<!-- First, to what degree does the social scale of relationships, spatial -->
<!-- scale of landscapes, and temporal scale of analysis influence our ability to -->
<!-- interpret complex social systems?  -->
<!-- Second, can variation in the social, spatial, -->
<!-- and temporal scale improve predictions associated with biological differences in -->
<!-- seasonal resource availability and social association?  -->

@@

## Etc
The integration of behavioural and ecological theory has shown the value of
considering the importance of various ecological disciplines to better
understand and predict animal social networks, including demography
[@Shizuka_2019], evolutionary and quantitative genetics [@Fisher_2017], disease
ecology [@Silk_2017], and animal personality [@Sih_2018]. While the number of
studies integrating social network theory into a broader array of behavioural
and ecological sub-disciplines is impressive, only recently has the role of
animal space use been considered in describing the causes and consequences of
the social environment in the context of (1) phenotypes and individual fitness
[@Webber_2018], (2) movement ecology and collective movement [@Bode_2011], and
(3) habitat selection and space use [@He_2019]. Importantly, much of the work
linking space use and the social environment has been theoretical and empirical
studies are lacking [but see @Peignier_2019; @Strandburg_Peshkin_2015;
@Strandburg_Peshkin_2017]. Here, we discuss the role of scale and multilayer
networks in the emerging integration of social and spatial ecology within the
behavioural ecology literature.

## Movement ecology and collective movement

Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Movement as a collective group can reduce per capita
predation risk via detection-dilution trade-offs and improve information
transfer about the quality or location of resources to other group members
[@Jolles_2019]. We integrate proximity based social networks
that inherently rely on animal collective movement, and, in general, we found
that movement is likely an important mechanism driving social network
connectivity within and between habitat types.

<!-- fixed array -->
Although multilayer animal social networks are relatively novel [@Silk_2018],
movement behaviour within multilayer networks has been considered. Spatial
networks are physical locations (nodes) which are connected in a network when
individuals move between said locations (edges). For example, spatial networks
were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and
*Carcharhinus melanopterus*) between fixed location autonomous arrays. In this
example, nodes represent locations within the array, *intralayer edges*
represent individual movement frequency, and *interlayer edges* represent
contact probability among individuals at a given node [@Mourier_2019]. Although
movement between fixed arrays is inherent, networks are not constructed based on
continuous measures of dyadic or collective movement [@Long_2014]. Our
study builds on the work of Mourier et al. (2019) and explicitly integrates
continuous and simultaneous measures of animal movement through space and time
as layers of a multilayer social network.

In contrast to spatial networks, where nodes represent spatial locations that
are fixed in space, movement networks can represent continuous and simultaneous
movement trajectories of multiple animals. In a recent study of vulturine
gunieafowl (*Acryllium vulturinum*), GPS movement data were used to generate
monolayer association networks within a multilayer network [@Papageorgiou_2019].
However, despite potential to generate networks in different spatial or social
contexts, layers in the multilayer network represented social associations
within and between groups. Continuous collection of animal relocation data using
GPS technology can be used to measure how groups of animals make collective
movement decisions in the context of their local environment
[@Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017] and across scales. A
collective movement layer could constitute similarity in movement for dyads
[@Long_2014] or groups [@Bode_2011]. This movement layer could be made at a
fine [i.e. minute-to-minute: @Cleasby_2019] or coarse scale [global migration:
@Flack_2018].

>>>>

Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Movement as a collective group can reduce per capita
predation risk via detection-dilution trade-offs and improve information
transfer about the quality or location of resources to other group members
[@Jolles_2019]. Given the existing framework for constructing multilayer networks from
behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
quantify movement parameters could be integrated. For example, edges could
represent measures of dyadic or collective movement based on dynamic interaction
metrics [@Long_2014]. Integrating movement layers with habitat-specific social
association layers could further illuminate the role of movement as a driver
of the social and spatial environments an individual experiences [@Webber_2018].
We generated multilayer networks based on habitat-specific layers of 
social association. Coordinated movement of dyads, or groups, could vary based on
habitat, and the approach we outline could be used to explore mechanisms linking
the social and spatial environments. For example, social processes may be an
emergent property of the landscape because animals aggregate at resources, such
as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
patches or territories can also contribute to the formation of the social
environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
males interacted primarily at home range edges, presumably driving territorial
behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
network framework is a logical next step for a burgeoning field. In particular,
when association networks are habitat-specific, we suggest the integration of
movement and space use in multilayer networks provides novel insights into the
effects of habitat configuration on the formation of the social environment
[@He_2019; @Webber_2018].

@@

@@
